Deployable Probabilistic Programming

### 2019-04-18 paper/paper.tex
citations of dissertations and a note of comparison of probabilisti languages

Incorporating a probabilistic program, or rather a probabilistic
procedure, within a larger code body appears to be rather
straightforward: one implements the model in the probabilistic
programming language, fetches and preprocesses the data in the
host programming language, passes the data and the model to an
inference algorithm, and post-processes the results in the
host programming language again to make algorithmic
decisions based on inference outcomes. However, complex
software systems make integration of probabilistic
inference challenging.

>>>>

Incorporating a probabilistic program, or rather a probabilistic
procedure, within a larger code body appears to be rather
straightforward: one implements the model in the probabilistic
programming language, fetches and preprocesses the data in the
host programming language, passes the data and the model to an
inference algorithm, and post-processes the results in the host
programming language again to make algorithmic decisions based
on inference outcomes. To choose the best one for each particular
application, probabilistic programming languages and systems are
customarily compared by the expressive power (classes of
probabilistic models that can be represented), conciseness (e.g.
the number of lines of code to describe a particular model), and
time and space efficiency of inference
algorithms~\cite{WVM14,P16,R17,GXG18}.  However, complex
software systems make integration of probabilistic inference
challenging, and considerations between beyond expressiveness
and performance come into play.
